I developed two extensions to leverage 
the capabilities of \Cyclus to model
real-world fuel cycle transition scenarios.
The first extension is a python input-generating module
that automates scenario generation of the real-world 
nuclear fleet at any point in time. The second extension
is a \Cyclus archetype that mimics \gls{MSR} feed and removal
behavior using an HDF5 database generated from SaltProc.

\section{\texttt{cyclus-input-gen}}
\label{sec:writeinput}
The python package \texttt{cyclus-input-gen} contains
multiple submodules for automating \Cyclus input generation.
The submodule \texttt{from\_pris} automates the generation of \Cyclus input files
to model the state of reactor fleets at a given
point in time.

The script reads from the \glsfirst{PRIS} database \cite{iaea_nuclear_2018}
and extracts data about each reactor's country, reactor unit,
type, net capacity (MWe), status, operator, construction date,
first criticality date, first grid date, commercial date,
and shutdown date (if applicable). The user inputs simulation
configurations such as start year, start month, and
simulation duration. \texttt{from\_pris} uses the collected data to
fill out a template into a \Cyclus input file. 
Diagram \ref{diag:log_flow} shows the logical flow of the module.


\begin{figure}
	\centering
	\begin{tikzpicture}[node distance=3.5cm and 2cm, on grid, auto, text width=2cm]
	\node (database) [object] {PRIS Database (\texttt{.csv})};
	\node (data) [process, below of=database] {Reactor data (net capacity, reactor size)};
	
	\node (user) [object, right=7cm of database] {User};
	\node (input) [process, below of=user] {Start year, month,  Simulation duration};
	
	\node (script) [object, below right= 2cm and 3.5cm of data] {\texttt{from\_pris}};
	
	\node (lifetime) [process, below of=script] {Calculated reactor lifetime};
	\node (coresize) [process, right of=lifetime] {Interpolated core size};
	\node (region) [process, left of=lifetime] {Calculated deployment scheme};
	
	\node (output) [object, below of=lifetime] {Generated Cyclue Input File (.xml)};
	
	\draw [arrow] (database) -- (data); 
	\draw [arrow] (user) -- (input); 
	\draw [arrow] (data) -- (script);
	\draw [arrow] (input) -- (script);
	
	\draw [arrow] (script) -- (lifetime);
	\draw [arrow] (script) -- (coresize);
	\draw [arrow] (script) -- (region);
	
	\draw [arrow] (lifetime) -- (output);
	\draw [arrow] (coresize) -- (output);
	\draw [arrow] (region) -- (output);
	
	\end{tikzpicture}
	\caption{ Logic flow of \texttt{from\_pris}.
		Green circles and blue boxes represent files and data, respectively.}
	\label{diag:log_flow}
\end{figure}

\subsection{Reactor deployment calculation}
The module calculates the deployment
scheme of reactors and their lifetimes by assuming
that all reactors shut down after 60 years of operation.
If the expected shutdown date is later than the user-input
simulation start date,
the reactor is not written in the input. If the reactor was
operational prior to the simulation start date,
and its shutdown date later than simulation start date,
the reactor is deployed at the beginning of simulation with its remaining lifetime.
If the reactor's start date is later than the simulation
start date, and the shutdown time is undefined, the reactor
is deployed at the defined start date with 60 years of lifetime.

\subsection{Reactor parameter calculation}

The module calculates the core sizes of various reactor
types by using a linear core size model. It assumes that
the number of assemblies in a 
reactor core scales linearly from a model reactor design,
as shown in the equation below. The mass per assembly
is kept constant.
The model reactor designs are listed in table \ref{tab:lin_core}.

\[
A = A_{ref} \cdot \frac{\text{P}}{P_{ref}}
\]
\[
N_{assem.pwr} = 157 \cdot \frac{\text{P}}{1,100}
\]
\[
N_{assem.bwr} = 764 \cdot \frac{\text{P}}{10,098}
\]
\[
N_{assem.phwr} = 4,560 \cdot \frac{\text{P}}{700}
\]
\[
A = \text{number of assemblies in approximated core}
\]
\[
P = \text{power capacity of reactor}
\]

\begin{table}[h]
	\centering
	\caption{Reactor model designs used for the linear core size model.}
	\begin{tabularx}{\textwidth}{zzqqq|q}
		\hline
		\textbf{Category} & \textbf{Model Reactor} & \textbf{Power [MWe] ($P_{ref}$)} & \textbf{Assembly Mass [kg]} & \textbf{Assemblies in Core ($A$)} & \textbf{Reference}  \\
		\hline
		\gls{PWR} & AP-1000 & 1,110 & 446 & 157 & \cite{schulz_westinghouse_2006} \\
		\gls{BWR} & 4-MK I & 1,098 &180 & 764 & \cite{moore_physical_1989} \\
		\gls{PHWR} & CANDU6 & 700 & 24.17 & 4,560 & \cite{galeriu_technical_1999} \\
		\hline
	\end{tabularx}
	\label{tab:lin_core}
\end {table}


\section{saltproc\_reactor}
The SaltProc reactor is a \Cyclus facility archetype designed to 
model \gls{MSR} behavior using a database. It roughly couples ``SaltProc'' \cite{rykhlevskii_online_2017}
and \Cyclus, by using the output from SaltProc to mimic \gls{MSR}
feed and removal behavior in \Cyclus.

This method is similar to the simplified implementation of
recipe reactors, in which the depletion calculation is performed outside of the
fuel cycle simulation. Instead of a single depletion calculation
used in a recipe reactor, this reactor uses a database of recipes
to capture the continuously varying state of liquid-fueled reactors like \glspl{MSR}. 


\begin{figure}
	\centering
	\begin{tikzpicture}[node distance=3.5cm and 2cm, on grid, auto, text width=2cm]
	
	\node (msr) [object] {\gls{MSR} design};
	\node (repro) [object, right of = msr] {Reprocessing Scheme};
	\node (timesteps) [object, right of = repro] {Timesteps};
	
	\node (saltproc) [process, below of = repro] {SaltProc};
	\node (serpent) [process, right of = saltproc] {SERPENT 2};
	
	\node (hdf5) [object, below of = saltproc] {HDF5 Database};
	
	\node (hdf5 reactor) [process, below of = hdf5] {SaltProc -reactor};
	
	\node (bid) [object, below of = hdf5 reactor] {Feed Material request};
	\node (request) [object, right of = bid] {Waste Material bid};
	\node (power) [object, left of = bid] {Power};
	
	\node (cyclus) [process, below of = bid] {Cyclus};


	\draw [arrow] (msr) -- (saltproc); 
	\draw [arrow] (repro) -- (saltproc); 
	\draw [arrow] (timesteps) -- (saltproc);
	
	\draw [arrow] (saltproc) -- (serpent);
	\draw [arrow] (serpent) -- (saltproc);
		
	\draw [arrow] (saltproc) -- (hdf5);
	\draw [arrow] (hdf5) -- (hdf5 reactor);
	
	\draw [arrow] (hdf5 reactor) -- (bid);
	\draw [arrow] (hdf5 reactor) -- (request);
	\draw [arrow] (hdf5 reactor) -- (power);
	
	\draw [arrow] (bid) -- (cyclus);
	\draw [arrow] (request) -- (cyclus);
	\draw [arrow] (power) -- (cyclus);
	
	
	\end{tikzpicture}
	\caption{ Logic flow of \texttt{SaltProc Reactor}.
		Green circles and blue boxes represent files and data, respectively.}
	\label{diag:hdf5_flow}
\end{figure}

\subsection{Code description}
The user provides only of the commodity names
for each stream (e.g. waste, fertile), and the database path, since the
HDF5 database already contains the notion of reactor design,
reprocessing scheme, and other reactor parameters (shown in
figure \ref{diag:hdf5_flow}). The commodity names are needed
for reactor agents to communicate with other \Cyclus agents
in exchanging material.

At every timestep, 
The \texttt{SaltProc Reactor} calculates the material mass
and composition accumulated during the \Cyclus timestep,
as shown in equation below.

\[
M_{T} = \sum m_T
\]
\[
m_{T} = \sum_{t=(T-1)}^{T} m_{t}
\]
\[
M_T = \text{total mass of stream in one \Cyclus timestep}
\]
\[
m_T = \text{mass of isotope in one \Cyclus timestep}
\]
\[
m_t = \text{mass of isotope in one SaltProc timestep}
\]


\section{Limitation of the database approach}
\label{sec:limit}
The limitation of this database approach is that it does not
take into account the changing incoming fuel compositions due to decay.
The separated \gls{TRU} composition may vary depending on the duration
an \gls{LWR} \gls{UNF} assembly has been cooled, thus affecting the performance
of the \gls{MSR}. The database approach assumes a fixed input salt
composition, which is not the case in this simulation, because reprocessed
\gls{TRU} has varying decay times from discharge when it is fabricated and
put in the \gls{MSR}.

This limitation is similar to that of recipe reactors, in which the
fuel is transmuted to a pre-generated recipe regardless of the
incoming fuel composition. For example, a recipe reactor
depleting a \gls{MOX} fuel would deplete the \gls{MOX} fuel
to the same composition regardless of its fresh fuel composition.

There are three alternative to the database approach that can
improve the accuracy of \gls{MSR} depletion modeling:
\begin{enumerate}
    \item Use collection of databases to cover varying incoming fuel composition
    \item Perform depletion calculations in \Cyclus via coupling with SaltProc
    \item Perform depletion calculations in \Cyclus using \glspl{ROM} of depletion codes
\end{enumerate}

The first method can take into
account the varying incoming fuel compositions by implementing
multiple SaltProc outputs instead of one. In this method,
upon receiving initial fuel, \Cyclus would identify the SaltProc output with 
the initial fuel composition closest to that of the received fuel,
which will be more accurate than having only one database that 
represents one initial composition.
However, this method will be difficult
to be effective due to the large range of variations that the \gls{MSR}
initial fuel composition can have.

The second method to couple \Cyclus with SaltProc can improve
the inaccuracy from varying input fuel compositions, since
the exact composition of the fuel received by the reactor facility
is depleted in SaltProc, rather than assuming an initial
composition. However,
since fuel cycle analyses model multiple facilities simultaneously,
the computational burden required to run multiple SaltProc
simulations simultaneously inside a \Cyclus simulation
will outweigh its benefits. Because fuel cycle
analyses aim to obtain a `good-enough' approximation of a large
system, coupling \Cyclus with a high-fidelity model and
largely increasing the computational burden and simulation
time is not preferred.

A compromise of the two previously mentioned methods
is implementing a \gls{ROM} of a high-fidelity
depletion model in \Cyclus. 
A \gls{ROM} is a statistically trained algorithm that
defines a feature space (input parameters) and a
target space (output values).
The benefit of a \gls{ROM} is the reduction in computational
burden. A \gls{ROM} can be trained by training from a set of
SERPENT depletion results, where the feature space is the
input of the simulation, and output is the depleted fuel
composition (shown in figure \ref{diag:rom_flow}. 
The difficulty of creating a \gls{ROM} for depletion calculations
is that the feature space and the target space is very large, since
the feature and target space comprise of the composition of
every isotope.


\begin{figure}
    \centering
    \begin{tikzpicture}[node distance=3.5cm and 2cm, on grid, auto, text width=2cm]
    \node (incomp) [object] {Input composition ($\approx$ 1,000 isotopes)};
    \node (t) [object, below of=incomp] {depletion time};
    \node (powdens) [object, below of=t] {power density};
    
    \node (serpent) [process, right of=t] {SERPENT (ROM)};

    \node (outcomp) [objectr, right of=serpent] {Output composition ($\approx$ 1,000 isotopes)};

    \draw [arrow] (incomp) -- (serpent); 
    \draw [arrow] (t) -- (serpent); 
    \draw [arrow] (powdens) -- (serpent);
    \draw [arrow] (serpent) -- (outcomp);

    \end{tikzpicture}
    \caption{Example of a \gls{ROM} generated from SERPENT
             results. The green objects represent the feature
             space, and the red objects represent the
             target space. This example assumes that the
             geometry (and any other parameter) is the same for all SERPENT simulations.}
    \label{diag:rom_flow}
\end{figure}

In conclusion, each method for modeling \gls{MSR} depletion
in a large scale fuel cycle simulation has unique
benefits and drawbacks. The currently implemented method
of using a database generated from a high-fidelity depletion
tool has its limitations, but is adequate for a fuel cycle simulation,
due to its low computational burden and medium fidelity.