
%% Package and Class "uiucthesis2014" for use with LaTeX2e.
\documentclass{article}

\usepackage[acronym,toc]{glossaries}
\include{acros}
\usepackage{placeins}
\usepackage{booktabs} % nice rules (thick lines) for tables
\usepackage{microtype} % improves typography for PDF
\usepackage{xspace}
\usepackage[hidelinks]{hyperref}
\usepackage{xspace}
\usepackage{hhline}
\usepackage{amsmath}
\usepackage{color}
\usepackage{multirow}
\usepackage{fourier}
\usepackage{booktabs}
\usepackage{threeparttable, tablefootnote}

%tikzpicture fit to page width
\usepackage{environ}
\makeatletter
\newsavebox{\measure@tikzpicture}
\NewEnviron{scaletikzpicturetowidth}[1]{%
  \def\tikz@width{#1}%
  \def\tikzscale{1}\begin{lrbox}{\measure@tikzpicture}%
  \BODY
  \end{lrbox}%
  \pgfmathparse{#1/\wd\measure@tikzpicture}%
  \edef\tikzscale{\pgfmathresult}%
  \BODY
}

\usepackage{tabularx}
\newcolumntype{b}{>{\hsize=1.0\hsize}X}
\newcolumntype{s}{>{\hsize=.5\hsize}X}
\newcolumntype{m}{>{\hsize=.75\hsize}X}
\usepackage{graphics}
\newcommand{\Cyclus}{\textsc{Cyclus}\xspace}%
\newcommand{\uthree}{\xspace $^{233}_{92}U$ \xspace}
\newcommand{\ufive}{\xspace $^{235}_{92}U$\xspace}%%
\newcommand{\utwo}{\xspace $^{232}_{92}U$\xspace}
\newcommand{\ueight}{\xspace $^{238}_{92}U$\xspace}
\newcommand{\pu}{\xspace$^{239}_{94}Pu$\xspace}
\newcommand{\thor}{\xspace $^{232}_{90}Th$\xspace}
\graphicspath{ {images/} }
\usepackage[affil-it]{authblk}
\usepackage[numbers]{natbib}
\usepackage{notoccite}
\usepackage{tikz}
\usetikzlibrary{positioning, arrows, decorations, shapes}

\usetikzlibrary{shapes.geometric,arrows}
\tikzstyle{process} = [rectangle, rounded corners, minimum width=2.5cm, minimum height=1cm,text centered, draw=black, fill=blue!30]
\tikzstyle{object} = [ellipse, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=green!30]
\tikzstyle{empty} =  [rectangle, rounded corners, minimum width=2.5cm, minimum height=0.7cm,text centered, draw=black, fill=white!30]
\tikzstyle{arrow} = [thick,->,>=stealth]
\usepackage{cleveref}
\usepackage{datatool}


\begin{document}

\title{Sustainability Analysis of Thorium Fuel Cycles}
\author{Jin Whan Bae}


%% Create an abstract that can also be used for the ProQuest abstract.
%% Note that ProQuest truncates their abstracts at 350 words.
\begin{abstract}
This work measures different sustainability metrics of various
thorium fuel cycles, through a SERPENT, a high-fidelity reactor core
code, coupled with CYCLUS, an agent-based fuel cycle simulator.
\end{abstract}

%% Create a dedication in italics with no heading, centered vertically
%% on the page.
%% Create an Acknowledgements page, many departments require you to
%% include funding support in this.
\chapter*{Acknowledgments}


%% The thesis format requires the Table of Contents to come
%% before any other major sections, all of these sections after
%% the Table of Contents must be listed therein (i.e., use \chapter,
%% not \chapter*).  Common sections to have between the Table of
%% Contents and the main text are:
%%
%% List of Tables
%% List of Figures
%% List Symbols and/or Abbreviations
%% etc.

\tableofcontents
\listoftables
\listoffigures

%% Create a List of Abbreviations. The left column
%% is 1 inch wide and left-justified
\chapter{List of Abbreviations}
\printglossaries
%% Create a List of Symbols. The left column
%% is 0.7 inch wide and centered
\chapter{List of Symbols}


\pagebreak

\section{Background}
From the early years of nuclear power, thorium has been
considered as a candidate for an alternative to uranium
for nuclear fuel. However, due to restrictions on reprocessing
and the sole adoption of \glspl{LWR} for commercial nuclear
power plants suppressed both research and interest in the 
thorium fuel cycle. 

Recently, however, with the realization of the limited
uranium resource, and a heightened interest on advanced
reactors and fuel cycles, the thorium fuel cycle is
dubbed by the media as the key to make nuclear power
more sustainable and safe. There is considerable interest
in nations like China, U.S., and especially India.
India has a large thorium reserve in it south coastal regions,
making the adoption of thorium fuel cycle an attractive option
for India to achieve energy independence.

Thorium is not fissile. Thorium is \textbf{fertile}, meaning
it only has the possibility to become a fissile isotope after
series of neutron absorption and decay. The stages of Th-232
becoming a fissile isotope, U-233, is illustrated in \cref{diag:th_chain}. 

\begin{figure}[h]
\caption{Th-232 chain to U-233}
\label{diag:th_chain}
\begin{scaletikzpicturetowidth}{\textwidth}
\begin{tikzpicture}[scale=\tikzscale, node distance=3.3cm]
\node (th232) [process] {n + $^{232}_{90}Th$};
\node (th233) [process, right of=th232] {$^{233}_{90}Th$};
\node (pa233) [process, right of=th233]{$^{233}_{91}Pa + \beta^{-}$};
\node (u233) [process, right of=pa233]{$^{233}_{92}U + \beta^{-}$};

\draw [arrow] (th232) -- (th233); 
\draw [arrow] (th233) -- (pa233);
\draw [arrow] (pa233) -- (u233);

\end{tikzpicture}
\end{scaletikzpicturetowidth}
\end{figure}


\section{Introduction}

Nuclear fuel cycles are defined by various parameters. The more important
parameters are: fuel type, reactor type, spectrum, breeding ratio, and stages, and goal
(organized in table \ref{tab:fc_param}).

\begin{table}[h]
    \centering
                \begin{tabularx}{\textwidth}{lbb}
                    \hline 
                    \textbf{Fuel Cycle Parameters} & \textbf{Detail} & \textbf{Example}\\
                    \hline
                    \hline
                    Isotope & Natural feed and fissile material & \ueight + Pu , \thor + \uthree \\
                    Reactor Type & Type of coolant, fuel form & \gls{MSR}, \gls{SFR}, \gls{PWR} \\ 
                    Spectrum & Neutron spectrum in reactor. Moderator. &  Fast, thermal, epithermal \\
                    Breeding Ratio & Fissile isotope composition after irradiation & >1 (breeder) , <1 (burner) \\
                    Stages & How many reactors and phases it involves & Multi-stage (\gls{SFR} \& MOX LWR (EG30)), Single-stage (Closed \gls{SFR}) \\
                    Goal & What the fuel cycle aims to do & Reduce \gls{MA} discharge, eliminate enrichment need\\
                    \hline
                \end{tabularx}
    \caption { Fuel Cycles are defined by the following parameters.}
    \label{tab:fc_param}

\end{table}



Some of the claims made by papers fail to capture
the entire picture of the fuel cycle, considering they have different
technologies used for each fuel cycle. For example, it is difficult
to compare the `superiority' of a fuel cycle by comparing the 
\gls{LWR} \gls{UNF} of radiotoxicity, since the technologies
representing the fuel cycle is different.

%da fa
The thorium fuel cycle to look at is, namely the EG38
from the Nuclear Fuel Cycle Evaluation and Screening Study \cite{wigeland_nuclear_2014},
which is the continuous recycle of $^{233}U/Th$ with new
Th fuel in both fast and thermal critical reactors.
The reactors that will be used is the \gls{MSBR} \cite{robertson_conceptual_1971},
which includes an online reprocessing facility that
continuously remove \glspl{FP} and \glspl{MA} from the core
and refuels the bred \uthree to maintain criticality. 
The neutrons are moderated by graphite for better breeding.


The uranium-plutonium fuel cycle to be compared is the 
EG23, continuous recycle of U/Pu with new natural uranium
fuel in fast critical reactors. The reactor that will be used
is the \gls{SFR}, with oxide fuel. The \gls{MOX} fuel will 
breed plutonium, which will be recycled into the \gls{SFR}.
The \glspl{FP} and \glspl{MA} will be disposed, and the 
mass loss will be filled with natural uranium.

For a fair comparison, the breeding ratio of the two
reactors should be similar.

\section{Method}

The goal of this study is to calculate sustainability
metrics of the two advanced fuel cycles for comparison.
First, SERPENT simulations of both the \gls{MSBR} and \gls{SFR}
are run with varying parameters. These results are run
through RAVEN \cite{rabiti_mathematical_2013} to generate
a \gls{ROM}, which is then implemented into a \Cyclus
archetype. This \Cyclus archetype then acts as a reactor
module that mimics SERPENT code in executing depletion
calculations as well as output reactor metrics.

Unlike the E\&S Study, this study looks at the 
fuel cycle in a transition scenario, and assesses
the viability and speed of transition as well as
the sustainability metrics of the fuel cycle at equilibrium.

Sustainability metrics are defined as how less of an requirement
from outside sources the fuel cycle needs. Traditional fuel cycle
metrics are: natural resource utilization, natural resource
usage per energy generation, spent fuel and waste radiotoxicity
and volume.  Additionally, for advanced fuel cycles,
it is necessary to consider all stages of the fuel cycle,
namely reprocessing. Reprocessing takes a large part of the 
cost of advanced fuel cycle. A careful analysis of not only
the economic cost but also the externalities such as the health and societal cost of 
reprocessing should be analyzed for a fuller picture.


\section{Literature Review}

\subsection{Similar Work}
Similar work to this paper, or papers that quantify
sustainability metrics of thorium and uranium fuel cycles include:
\begin{itemize}
\item Transmutation difference in \gls{PWR}, \gls{MSR}, \gls{SFR}, \gls{LFR} \cite{becker_transmutation_2007}
    \item Thorium fuel cycle with different reactors and spectra (\gls{LWR}, \gls{MSR}, \gls{SFR}) using SCALE/TRITON \cite{brown_sustainable_2015}. This paper concludes that overall, fuel cycle performance is expected to be similar for fast and intermediate spectrum critical reactors in equilibrium.
    \item Various thorium fuel cycle with different reactor designs and recycle schemes and recycle stream utilization \cite{taiwo_thorium_2016} \cite{krahn_-ne0000735_2017}.
    \item Evaluation and Screening of 40 evaluation groups \cite{wigeland_nuclear_2014} in an equilibrium fuel cycle.
\end{itemize}

No identified work on comparing U-Pu and Th-U fuel cycles
in a transition scenario, given similar technology, was found. Most papers
offer short-term metrics (e.g. spent fuel radiotoxicity, feed rate) 
for different fuel cycles but not the entire picture.

\subsection{Reactors for Thorium Fuel Cycles}

Thorium's ability to breed \uthree in the thermal spectrum allows
it to used in almost all types of reactors, including \gls{LWR} reactors
such as \glspl{PWR} (listed in table \ref{tab:reactors}.
 Many papers claim the benefit of using thorium
in the current fleet of \glspl{LWR} to reduce radiotoxicity of used fuel
and enrichment demand.

\begin{table}[h]
    \centering
                \begin{tabularx}{\textwidth}{sb}
                    \hline 
                    \textbf{Reactor Type} & \textbf{References} \\

                    \hline
                    \hline
                    
                    \multirow{ 2}{*}{\gls{SFR}} & SUPER-PRISM (GE) \cite{carroll_super-prism_2002} \\
                     & \gls{ASTRID} \cite{varaine_pre-conceptual_2012} \\ 
                     
                    \hline
                    
                    \multirow{2}{*}{\gls{MSR}} & \gls{MSBR} \cite{robertson_conceptual_1971} \\
                     & MSFR \cite{fiorina_molten_2013} \\
                    
                    \hline
                    
                    \gls{HWR} & CANDU-type\cite{boczar_thorium_2002} \cite{bromley_multiregion_2016} \cite{golesorkhi_simulations_2016} \\

                    \hline

                    \gls{LWR} & \gls{PWR} \cite{ade_analysis_2016}\\
                    \hline
                \end{tabularx}
    \caption {Table of reactors used in thorium fuel cycle studies. The ability of thorium
             to breed in the thermal spectrum allows the utilization of various various reactor types.}
    \label{tab:reactors}
\end{table}


\subsection{Sustainability Metrics from Nuclear Fuel Cycle Studies}

From the nuclear fuel cycle domain, sustainability metrics can be
divided into four categories: fuel, back-end, fuel cycle, and 
economic sustainability. The metrics are mostly quantitative,
but some are qualitative (organized in table \ref{tab:sus_met}).

\begin{table}[h]
    \centering
    \begin{tabularx}{\textwidth}{lb}

    \hline

    \textbf{Category} & \textbf{Metrics [unit]} \\

    \hline
    \hline

    \multirow{2}{*}{Fuel Sustainability} 
     & Availability in nature [t] \\
     & Energy per mass of feed [MW/t] \\
    
    \hline

    \multirow{6}{*}{Back End Sustainability} 
     & Proliferation resistance \\
     & \gls{UNF} mass disposed per energy [t/MW] \\
     & \gls{HLW} mass disposed per energy [t/MW] \\
     & \gls{LLW} mass disposed per energy [t/MW] \\
     & Radiotoxicity of \gls{UNF} per mass [Ci/t] \\
     & Decay heat of \gls{UNF} per mass [W/t] \\

    \hline

    \multirow{4}{*}{Fuel Cycle Sustainability}
     & Worker does per energy [Ci/MW] \\
     & Enrichment requirement per energy [SWU/MW] \\
     & Reprocessing requirement per energy [?] \\
     & Water use per energy generated [t/MW] \\
    \hline

    Economic Sustainability
     & \gls{LCOE} [\$/MW] \\

    \hline
    \end{tabularx}
    \caption {Table of sustainability metrics obtained from literature \cite{wigeland_nuclear_2014} \cite{gonzalez_methodology_2003} \cite{allibert_introduction_2015}}
    \label{tab:sus_met}
\end{table}

\subsection{Sustainability Metrics in Other Domains}

These are part of the sustainability metrics obtained from the principles
of green chemistry, from \cite{gonzalez_methodology_2003}:
\begin{itemize}
    \item Less hazardous chemical syntheses
    \item Use of renewable feedstocks
    \item Accident prevention
    \item Reduce derivatives
    \item Design for degradation
    \item Full mass balance
    \item Conversions
    \item Exotherms
    \item Waste emitted to air
    \item Operator safety
\end{itemize}

\noindent Another sustainability metric for business decision making, from \cite{schwarz_use_2002}:
\begin{itemize}
    \item Energy per mass
    \item Water
    \item pollutants
\end{itemize}


\subsection{Differences in U and Th Fuel Cycles}
Fundamental differences in uranium and thorium fuel
cycles have been discussed in various literature,
their topics ranging from 
non-proliferation
\cite{iaea_thorium_2005} 
\cite{moir_recommendations_2008} 
\cite{kang_u-232_2001} %this guy is skeptical of it
,
availability
\cite{herring_uranium_2013}
,
better neutronic properties (moreso at higher temperatures)
\cite{lung_perspectives_1998}
,
thermal breeding capability
\cite{robertson_conceptual_1971}
,
and 
radiotoxicity of spent fuel
\cite{croff_comparative_2016}
.


Other important fuel cycle benefit metrics
such as safety is usually attributed heavily
to reactor design, not the fuel. In other words,
it could be said that thorium-fueled \glspl{MSR} are safer
than uranium-fueled \glspl{LWR}, but it is hard to claim
that thorium fuels are inherently `safer' than uranium fuels.


\subsection{Proliferation Resistance}
Thorium is claimed to have a higher proliferation resistance
due to its diversion barriers. The barriers can be divided into
two categories - intrinsic and extrinsic. Material barriers
are qualities that make it difficult to produce a weapon related
to the composition of the material, along with the difficulty of
access to the material. The IAEA defines a fissile material's weapon
quality by the following three properties: critical mass, spontaneous 
fission yield (weapon degradation), and heat emission \cite{iaea_thorium_2005}.
Although \uthree has a lower spontaneous fission rate and decay heat per kilogram,
it has a higher critical mass than that of \pu and is harder to separated.
Thorium breeding leads to a mixture of different uranium isotopes including
\utwo, which is a 2.6 MeV gamma emitter \cite{moir_recommendations_2008}. This hard gamma emitter provides
both a diversion and fabrication barrier, as well as increase the material's detectability
Also, \uthree can be easily denatured by adding abundant natural uranium, while
there is no comparable denaturing method for plutonium \cite{kang_u-232_2001}.


\subsection{Availability}
It is estimated that thorium is about 3.9 times more abundant in
nature than uranium \cite{herring_uranium_2013} in land reserves. However, there
is an estimated 4.6 billion tons of uranium, which is about a thousand
times larger than the identified land reserve \cite{agency_uranium_2010}.
However, uranium extraction from seawater is currently not economical \cite{tamada_cost_2006}.
There are thorium in seawater as well, but its concentration is four orders of magnitude
lower than that of uranium \cite{bardi_extracting_2010}. 

\subsection{Better Neutronic Properties}
The benefits of thorium can be looked at from a neutronics standpoint.
First, thorium can be bred relatively efficiently into \uthree in thermal spectrums,
which allow for breeding reactors with comparable conversion ratios \cite{allibert_introduction_2015}.
\uthree also has a higher eta($\eta$) ratio of neutron yield per fission to 
neutrons absorbed than that of \ufive and \pu \cite{lung_perspectives_1998}.
\uthree maintains good neutronic properties in high temperatures,
which make it an attractive fuel for high temperature reactors, which
are the majority of GEN-IV reactors.

\subsection{Radiotoxicity of Spent Fuel}
Two components contribute to the radiotoxicity of 
\gls{UNF}: \glspl{FP} and \glspl{MA}.
Fission products account for the majority of early (\textasciitilde 500 years)
\gls{UNF} radiotoxicity, while \glspl{MA} account for 
radiotoxicity into geological time.
Studies claim that thorium fuel cycle produces relatively
less plutonium and \gls{MA} \cite{boczar_thorium_2002} \cite{david_revisiting_2007},
which leads to a lower long-term radiotoxicity and repository safety.
However, some studies show that given the same technology (eg. \gls{PWR} Breed-and-burn),
\uthree - Th and \pu - \ueight fuels produce similar radiotoxicity \cite{croff_comparative_2016}.

In short, many papers that claim the drastic improvement that the thorium
fuel cycle will bring assumes a thorium cycle in part of a GEN-IV system,
not doing complete fairness to the uranium-plutonium fuel cycle. However,
there is potential merit and a fair reason to pursue the thorium fuel cycle.
Thus, this paper will compare the two fuel cycles given comparable technology
advancement. 


%\chapter{Conclusions}


%\appendix*
%\include{Appendix.tex}

\section{Fuel Cycles to Compare}
\begin{itemize}
\item MSBR Th-U3, with natural Th feed \cite{robertson_conceptual_1971}
\item MSBR U8-Pu, with natural U feed
\item SFR Th-U3, with natural Th feed
\item SFR U8-Pu, with natural U feed
\end{itemize}


\section{Flow Chart of \gls{CORRM}}

\tikzstyle{decision} = [diamond, draw, fill=blue!20, 
    text width=5em, text badly centered,  inner sep=0pt]
\tikzstyle{block} = [rectangle, draw, fill=blue!20, 
    text width=8em, text centered, rounded corners, minimum height=3em]
\tikzstyle{buff} = [rectangle, draw, fill=green!20, 
    text width=8em, text centered, rounded corners, minimum height=3em]
\tikzstyle{kernal} = [rectangle, draw, fill=red!20, 
    text width=8em, text centered, rounded corners, minimum height=3em]
\tikzstyle{line} = [draw, -latex']
\tikzstyle{dummy} = [rectangle]
\tikzstyle{cloud} = [draw, text centered, ellipse,fill=red!20, text width=15em,
    minimum height=2em]

\usetikzlibrary{calc}

\begin{figure}[!ht]
\begin{tikzpicture}[node distance = 2.5cm and 2cm, auto]
    % Place nodes
    \node [kernal] (enternotify) {Set buy policy};
    \node [block, below of=enternotify] (tick1) {Empty tick?};
    \node [kernal, below of=tick1] (dre) {DRE - receive fuel and fill};
    \node [decision, below of=dre] (core?) {Is core Loaded?};
    \node [block, right = of dre] (tock) {Shutdown State - Do nothing};
    \node [decision, below of=core?] (crit1) {Critical?};
    \node [block, left = of crit1] (fiss) {Ask for more fissile?};
    \node [block, below of=crit1] (dep) {Deplete using ROM};
    \node [buff, below of=dep] (torep) {Core to Rep};
    \node [block, right = of torep] (rep) {Separate};
    \node [buff, below of=torep] (refill) {Refill Core from fill tank};
    \node [buff, right = of dep] (waste) {Add separated waste to waste for market};
    \node [buff, right = of refill] (backto) {Send fuel isotope back into core};
    \node [buff, right = of rep] (patank) {Pa tank for decay};
    \node [block, right = of backto] (decay) {Decay until Useful};
    \node [decision, below of=refill] (crit2) {Critical?};
    \node [buff, below of=decay] (backto2) {Send fuel isotope back into core};


    % Draw edges
    \path [line] (enternotify) -- (tick1);
    \path [line] (tick1) -- (dre);
    \path [line] (core?) -| node [near start] {no} (tock);
    \path [line] (tock) |- (tick1);
    \path [line] (dre) -- (core?);
    \path [line] (core?) -- node {yes} (crit1);
    \path [line] (crit1) -- node {yes} (dep);
    \path [line] (crit1) -- node {no} (fiss);
    \path [line] (dep) -- (torep);
    \path [line] (torep) -- (refill);
    \path [line] (refill) -- (crit2);
    \path [line] (torep) -- (rep);
    \path [line] (rep) -- (waste);
    \path [line] (rep) -- (patank);
    \path [line] (rep) -- (backto);
    \path [line] (backto) -- (crit2);
    \path [line] (patank) -- (decay);
    \path [line] (decay) -- (backto2);
    \path [line] (backto2) -- (crit2);
    \path [line] (crit2.south) |- node {no} ($(crit2.south) - (0,5mm)$) -|  (fiss);
    \path [line] (crit2.west) -| node {yes} ($(crit2.west) - (10mm, 0)$) |-  (dep);
    

    

    %\path [line] (decide) -| node [near start] {yes} (update);
    %\path [line] (update) |- (identify);
    %\path [line] (decide) -- node {no}(stop);
    \end{tikzpicture}
\caption{\color{red}{Kernal Interactions}, \color{blue}{In-agent functions}, 
         \color{green}{Buffer Transactions}.}
\end{figure}

\bibliographystyle{unsrtnat}
\bibliography{bibliography}


\end{document}
\endinput
%%
%% End of file `thesis-ex.tex'.
