
%%
%% This is file `thesis-ex.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% uiucthesis2014.dtx  (with options: `example')
%% 
\def\fileversion{v2.25b} \def\filedate{2018/06/10}
%% Package and Class "uiucthesis2014" for use with LaTeX2e.
\documentclass[edeposit,fullpage]{uiucthesis2014}

\usepackage[acronym,toc]{glossaries}
\include{acros}
\usepackage{placeins}
\usepackage{booktabs} % nice rules (thick lines) for tables
\usepackage{microtype} % improves typography for PDF
\usepackage{xspace}
\usepackage[hidelinks]{hyperref}
\usepackage{xspace}
\usepackage{setspace}
\usepackage{hhline}
\usepackage{amsmath}
\usepackage{color}
\usepackage{multirow}
\usepackage{fourier}
\usepackage{booktabs}
\usepackage{threeparttable, tablefootnote}

\usepackage{graphics}
\newcommand{\Cyclus}{\textsc{Cyclus}\xspace}%
\newcommand{\uthree}{\xspace $^{233}_{92}U$ \xspace}
\newcommand{\ufive}{\xspace $^{235}_{92}U$\xspace}%%
\newcommand{\utwo}{\xspace $^{232}_{92}U$\xspace}
\newcommand{\ueight}{\xspace $^{238}_{92}U$\xspace}
\newcommand{\pu}{\xspace$^{239}_{94}Pu$\xspace}
\newcommand{\thor}{\xspace $^{232}_{90}Th$\xspace}
\graphicspath{ {images/} }
\usepackage[affil-it]{authblk}
\usepackage[numbers]{natbib}
\usepackage{notoccite}
\usepackage{tikz}
\usetikzlibrary{positioning, arrows, decorations, shapes}

\usetikzlibrary{shapes.geometric,arrows}
\tikzstyle{process} = [rectangle, rounded corners, minimum width=2.5cm, minimum height=1cm,text centered, draw=black, fill=blue!30]
\tikzstyle{object} = [ellipse, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=green!30]
\tikzstyle{empty} =  [rectangle, rounded corners, minimum width=2.5cm, minimum height=0.7cm,text centered, draw=black, fill=white!30]
\tikzstyle{arrow} = [thick,->,>=stealth]
\usepackage{cleveref}
\usepackage{datatool}


\begin{document}

\title{Key Parameters and Metrics of Fuel Cycle Transitions}
\author{Jin Whan Bae}
\department{Nuclear, Plasma, Radiological Engineering}
\schools{B.S., University of Illinois at Urbana-Champaign, 2017}
\msthesis
\advisor{Kathryn Huff}
\degreeyear{2018}
\committee{Professor Kathryn Huff, Advisor}
\maketitle

\frontmatter

%% Create an abstract that can also be used for the ProQuest abstract.
%% Note that ProQuest truncates their abstracts at 350 words.
\begin{abstract}
This work identifies important metrics and parameters in
nuclear fuel cycle transition scenarios. First, the agent-based
fuel cycle simulator \Cyclus is benchmarked against \gls{ORION}.
Second, important fuel cycle transition metrics are identified
by extensive literature review.
Third, I run sensitivity studies on two regional fuel cycle
transition scenarios (U.S. and France) to identify important
parameters and how they affect the metrics.
[results]
\end{abstract}

%% Create a dedication in italics with no heading, centered vertically
%% on the page.
\begin{dedication}
To children worldwide.
\end{dedication}

%% Create an Acknowledgements page, many departments require you to
%% include funding support in this.
\chapter*{Acknowledgments}

I consider all my output as a result of me standing on the shoulder
of giants. There have been multiple giants that were kind enough
to lend me their shoulders. Notably, the tallest of all, my advisor
and mentor Kathryn Huff, who patiently guided me from my academic
infancy. Also, I owe the world to my parents and loving brother brought me up with love
from my actual infancy.  I also thank the staff of Oak Ridge National Laboratory
Joushua L. Peterson-Droogh, Eva Davidson, and Andrew Worrall for their
guidance over the summer.

I also cannot express enough gratitude to my friends and colleagues. My greatest
assets and partners that I have had the privilege to cohabitate with, Daniel
O'Grady and Steven Stemmley, who were the logical anchor in my life. Also, my colleagues
Andrei Rykhlevskii, Gwendolyn Chee, Gregory Westphal, Gyu Tae Park, Sun Myung Park, and
Anshuman Chuabe have been of great help. Lastly thanks to my long friends Shane Riew,
Eric Bae, Daniel Stewart, and all my comrades from the 12DIV Engineering 3CO.

\tableofcontents
\listoftables
\listoffigures

%% Create a List of Abbreviations. The left column
%% is 1 inch wide and left-justified
\chapter{List of Abbreviations}

\begin{symbollist*}
\printglossaries
\end{symbollist*}

\mainmatter


\chapter{Background}
\input{background}

\chapter{Introduction}
\input{introduction}

\chapter{Literature Review}
\input{litrev}

\chapter{\Cyclus}
\input{cyclus}

\chapter{Method}
\input{method}

\FloatBarrier


\chapter{France}
\input{france}


\chapter{United States}
\input{us}

\chapter{Appendix}
\input{appendix}



\bibliographystyle{unsrtnat}
\bibliography{bibliography}

\end{document}
\endinput
%%
%% End of file `thesis-ex.tex'.
